---
title: "AoTSentiment_Analysis"
author: ""
date: "06-03-2022"
output: html_document
---

loading the libraries
```{r}
library(tidyverse)
library(readxl)
library(data.table)
library(sentimentr)
library(plotly)
library(RedditExtractoR)
library(lubridate)

```

picking the reddit links I'll use
```{r}

SnK.links<-c("https://www.reddit.com/r/anime/comments/s023oa/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/s5lab5/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/sayg2x/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/sgi8hb/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/sm2k98/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/sro7oz/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/sx6p4j/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/t2totg/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/t83w71/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/tdg2m4/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/tiurmj/shingeki_no_kyojin_the_final_season_part_2/","https://www.reddit.com/r/anime/comments/tvjj0i/shingeki_no_kyojin_the_final_season_part_2/")


```

collecting the info from the reddit links
```{r}

Shingeki = data.frame()

Shingeki.Threats=data.frame()


for(i in 1:length(SnK.links)) { 
  

content<-get_thread_content(SnK.links[i])

comments<-content[["comments"]]

threads<-content[["threads"]]

Shingeki <- rbind(Shingeki,comments)

Shingeki.Threats<-rbind(Shingeki.Threats,threads)
  
}

```

bar plot with word frequency per reddit comment
```{r}
Shingeki %>% mutate(words=str_count(comment,"\\w+")) %>% as_tibble() %>%filter(words<=100) %>%  ggplot(aes(x=words))+geom_bar()+theme_light()
  
```

table with word count per comment
```{r}
Shingeki %>%  mutate(words=str_count(comment,"\\w+")) %>% as_tibble() %>% count(words,sort=TRUE)
```

looking at comments with 1 word
```{r}

Shingeki %>%  mutate(words=str_count(comment,"\\w+")) %>% as_tibble() %>% filter(words==1) %>%  count(comment,sort=TRUE)

```


 
deleting junk from comments
```{r}
Shingeki1 <- Shingeki %>%
    as_tibble() %>%
    mutate(comment = str_replace_all(comment, "&quot;|&#x2F;", "'"),    
           comment = str_replace_all(comment, "&#x2F;", "/"),           
           comment = str_replace_all(comment, "<a(.*?)>", " "),          
           comment = str_replace_all(comment, "&gt;|&lt;", " "),        
           comment = str_replace_all(comment, "<[^>]*>", " "),
           comment = str_replace_all(comment,"http.*\\s*"," "),
           comment = str_replace_all(comment,"\\031","'"),
           comment = str_replace_all(comment,"\\[",""),
           comment = str_replace_all(comment,"\\]",""),
           comment = str_replace_all(comment,"\\(",""),
           comment = str_replace_all(comment,"\\)",""),
           comment = str_replace_all(comment,"\\*",""),
           comment = str_replace_all(comment,'"',""),
           comment = str_replace_all(comment,"~",""),
           comment = str_replace_all(comment,"#",""),
           comment = str_replace_all(comment,"\\n"," "),
           comment = str_replace_all(comment,"\\034",""),
           comment = str_replace_all(comment,"\\035",""),
           comment = str_replace_all(comment,"\\tI",""),
           comment = str_replace_all(comment,"_",""),
           comment = str_replace_all(comment,"\\\\"," "),
           comment = str_replace_all(comment,"a°",""),
           comment = str_replace_all(comment,"<",""),
           comment = str_replace_all(comment,">",""),
           comment = str_replace_all(comment,"&amp;",""),
           comment = str_replace_all(comment,"\\024",""),
           comment = str_replace_all(comment,"-",""),
           comment = str_replace_all(comment,"U\\+0096",""),
           comment = str_replace_all(comment,"\\033","")
           )         
```

deleting the comments by the user AutoModerator and comments with less than 5 words.
```{r}

Shingeki1<-Shingeki1 %>% mutate(words=str_count(comment,"\\w+")) %>% as_tibble() %>%filter(words>5&author!="AutoModerator")


```

deleting the words: rumblings, attack, paradise, dove and abnormal from the sentiment dictionary
```{r}

polarity_dt = lexicon::hash_sentiment_jockers_rinker

sentiment_key <- lexicon::hash_sentiment_jockers_rinker %>% 
  dplyr::filter(!x %in% c("rumbling","attack","paradise","dove","abnormal"))
```

adding the terms "talk no jutsu", "rushed" and "plot armor" as negative terms. There are probably more but I'm lazy
```{r}
custom_words<-data.table(
  x = c("talk no jutsu","rushed","plot armor" ),
  y = -1.00,
  key = "x")

sentiment_key2<-rbind(sentiment_key,custom_words)

sentiment_key2<-update_key(sentiment_key, x = data.frame(x = c("talk no jutsu","rushed","plot armor" ), y = c(-1, -1,-1)))

```

getting polarity scores
```{r}
mycomment <- get_sentences(Shingeki1$comment)

sentiments3<-sentiment_by(mycomment,polarity_dt = sentiment_key2)
```

creating an ID variable.
```{r}
Shingeki1<-Shingeki1 %>% mutate(element_id=1:5171)
```

joining sentiment scores to the main database
```{r}
Shingeki1<-inner_join(sentiments3,Shingeki1)
```
joining the  threat information to the main database
```{r}
Shingeki1<-inner_join(Shingeki1,Shingeki.Threats,by="url")
```

transforming the date variable (string) to a date format variable
```{r}
Shingeki1<-Shingeki1%>% mutate(date2=ymd(date.y),month=round_date(date2, "month"))
```

boxplot with polarity scores
```{r}
Shingeki1 %>% ggplot(aes(x=(ave_sentiment)))+geom_boxplot()
```

I used this code to analize comments with very high and very low sentiment score

```{r}
Shingeki1 %>%arrange(desc(ave_sentiment)) %>% select(comment)
```

 Plot using the "main" comments
```{r}
Shingeki1 %>%  filter((str_detect(.$comment_id,"_")==FALSE)) %>%  group_by(week=floor_date(date2, "week")) %>% 
  summarise(avg_sentiment=mean((ave_sentiment)))%>% 
  plot_ly( x = ~week) %>% add_trace(y = ~avg_sentiment, name = 'trace 0',mode = 'lines')%>% 
  layout(title = "Sentiment Analysis (Attack On Titan)")
```

I used this code to look at comments per date.
```{r}
Shingeki1 %>%  group_by(week=floor_date(date2, "week")) %>% filter(week=="2022-03-14")%>% filter((str_detect(.$comment_id,"_")==FALSE)) %>% select(comment,ave_sentiment,author.x) %>% arrange(desc(ave_sentiment)) 
```


Plot with all comments. I didn't use this.
``````{r}
Shingeki1 %>% group_by(week=floor_date(date2, "week")) %>% 
  summarise(avg_sentiment=mean(ave_sentiment))%>% 
  plot_ly( x = ~week) %>% add_trace(y = ~avg_sentiment, name = 'trace 0',mode = 'lines')%>% 
  layout(title = "Sentiment Analysis (Attack On Titan)")
```



filtering some words out of the emotions dictionary
```{r}
nrc_key <- lexicon::hash_nrc_emotions %>% 
  dplyr::filter(
  emotion %in% c('trust',"anger","anticipation","fear","sadness","surprise","disgust","joy")) %>% 
  dplyr::filter(!token %in% c("rumbling","attack","paradise","dove","abnormal"))
```

getting emotions
```{r}
emotions2<-emotion_by(Shingeki1$comment,emotion_dt =nrc_key)

```

Joining emotions to to main database
```{r}

Shingeki2<-inner_join(Shingeki1,emotions2,by="element_id")

```

plotting emotions with ggplot
```{r}

Shingeki2 %>% filter((str_detect(.$comment_id,"_")==FALSE))%>%  
  group_by(week=floor_date(date2, "week"),emotion_type) %>% 
  summarize(ave_emotion=mean(ave_emotion))%>% 
  filter(str_detect(emotion_type,"negated")==FALSE) %>% 
  ggplot(aes(x=week, y=ave_emotion,colour=emotion_type)) +
  geom_line() +facet_wrap(~emotion_type)+theme_light()+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```


Same plot with plotly
```{r}

emocion <- function(x) {
  Shingeki2 %>% 
  group_by(week=floor_date(date2, "week"),emotion_type) %>% 
  summarize(ave_emotion=mean(ave_emotion))%>% 
  filter(emotion_type==x) %>% select(ave_emotion)
  }
  

trust<-emocion("trust")
sadness<-emocion("sadness")
anticipation<-emocion("anticipation")
disgust<-emocion("disgust")
fear<-emocion("fear")
joy<-emocion("joy")
surprise<-emocion("surprise")
anger<-emocion("anger")


fecha<-trust %>% select(week)

data <- data.frame(fecha, trust, sadness,anticipation,disgust,fear,joy,surprise,anger)

plot_ly(data, x = ~week) %>% add_trace(y = ~ave_emotion, name = 'Trust',mode = 'lines')%>% 
  layout(title = "Sentiment Analysis (Polarity) 2020")%>% 
  add_trace(y = ~ave_emotion.1, name = 'Sadness',mode = 'lines') %>%  
  add_trace(y = ~ave_emotion.2, name = 'Anticipation',mode = 'lines') %>%  
  add_trace(y = ~ave_emotion.3, name = 'Disgust',mode = 'lines') %>%  
  add_trace(y = ~ave_emotion.4, name = 'Fear',mode = 'lines') %>%  
  add_trace(y = ~ave_emotion.5, name = 'Joy',mode = 'lines') %>%  
  add_trace(y = ~ave_emotion.6, name = 'Surprise',mode = 'lines')%>%  
  add_trace(y = ~ave_emotion.7, name = 'Anger',mode = 'lines')%>% 
  layout(title = "Sentiment Analysis By Emotions 2020")

```
```












